Reactor like TGE model

### 2019-04-14 AYSS-2019/presentation/main.tex
pre-final

\documentclass[8pt,pdf,hyperref={unicode}]{beamer}
% \documentclass[aspectratio=43]{beamer}
% \documentclass[aspectratio=1610]{beamer}
% \documentclass[aspectratio=169]{beamer}
\usepackage{lmodern}
\usepackage{amsfonts}
\usepackage{amsmath}

\graphicspath{{figures/}}

@@

\begin{document}
    % титульный слайд
    \begin{frame}
        \titlepage
    \end{frame}
\begin{frame}
   \frametitle{}

\begin{frame}
\frametitle{}

\begin{frame}
\frametitle{History}

@@

}%
\begin{frame}
    \frametitle{Reactor Like TGE model}
 \centering\includegraphics[width=0.8\paperwidth]{draw.pdf}

\end{frame}
\usebackgroundtemplate{}
\begin{frame}
\frametitle{Reactor Like TGE model}

@@

\begin{frame}
    \frametitle{Proof of concept}
   	For fast checking the potential of our idea, we considered a next simplified model:  
    \begin{itemize}
    	\item There are only one tuning parameter  --- the local coefficient of gamma multiplication, describing usefulness of atmosphere for generating secondary particles;
    	\item Production of Gamma in cell occurs by Poisson distribution, momentum direction of generated gamma is defined by the electric field direction;
    	\item Electric field is chaotic: in point of cell ignition, direction of field is generated by uniform distribution, but magnitudes is constant for whole cloud;
    	\item Energy of particle not taken into account, propagation of gamma simulated with exponential distribution with fixed mean free path;
    	\item Cloud size is equals 1 kilometer and tracking of particle leaving volume stopped. 
    \end{itemize}
    This model is implemented as program on Kotlin programming language.

\begin{frame}
    \frametitle{}
\begin{columns}
	\begin{column}{0.5\textwidth}
		\begin{figure}[htb]
		\centering
		\includegraphics[width=1\columnwidth]{proofTGF.pdf}
		\end{figure}
		The first figure shows the case of an explosive growth in the number of secondary photons that are well suited to the phenomenon of TGF.
	\end{column}
	\begin{column}{0.5\textwidth}
		\begin{figure}[htb]
			\centering
			\includegraphics[width=1\columnwidth]{Extinction.pdf}
		\end{figure}
		The second figure demonstrates the case when there was a dissipation of an avalanche that had just begun to develop.

@@

\begin{frame}
    \frametitle{}

@@

    	\begin{column}{0.5\textwidth}

    		\begin{figure}[htb]
    			\centering
    			\includegraphics[width=1\columnwidth]{proofTGE.pdf}
    		\end{figure}
    		The third figure demonstrates the case of a slower and less intensive growth. Such processes with some minor adjustments and assumptions about field dynamics could describe TGE phenomenon.	
    	\end{column}
    \end{columns}

>>>>

\documentclass[8pt,pdf,hyperref={unicode}]{beamer}
% \documentclass[aspectratio=43]{beamer}
% \documentclass[aspectratio=1610]{beamer}
% \documentclass[aspectratio=169]{beamer}
\usepackage{lmodern}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mwe,tikz}
\graphicspath{{figures/}}

@@

\begin{document}
    % титульный слайд
    \begin{frame}
        \titlepage
    \end{frame}
%\begin{frame}
%   \frametitle{}
% 
%\end{frame}
%
\begin{frame}
\frametitle{Thunderstorm cloud and lighting: paths for exploring}
    \begin{figure} \centering
    \begin{tikzpicture}[      
    every node/.style={inner sep=0pt},
    x=1mm, y=1mm
    ] 
    \node (fig0) at (0,50){
        \centering\includegraphics[width=0.15\paperwidth]{telescope.pdf}
    };
    \node (fig0t) at (0,38){
    Optical observations
    };   
    \node (fig1) at (95,90){ \centering\includegraphics[width=0.15\paperwidth]{satellite_r.pdf}
    };
    \node (fig0t) at (95,78){
    UV \& IR observations
    };  
    \node (fig2) at (0,90){
    \centering\includegraphics[width=0.15\paperwidth]{satellite_l.pdf}
    };  
    \node (fig0t) at (0,78){
    Gamma-rays
    }; 
    \node (fig3) at (50,70){
    \centering\includegraphics[width=0.2\paperwidth]{storm.pdf}
    };   
     \node (fig4) at (75,40){
        \centering\includegraphics[width=0.1\paperwidth]{antenna.pdf}
    }; 
    \node (fig5) at (95,45){
        \centering{\includegraphics[width=0.15\paperwidth]{dish.pdf}}
    };     
    \node (fig4t) at (95,30){
    VHS Interefemetry
    };
    \node (fig6) at (35,40){
    \centering{\includegraphics[width=0.1\paperwidth]{radio.pdf}}
    };
    \node (fig6) at (50,40){
    \centering{\includegraphics[width=0.1\paperwidth]{atom.pdf}}
    };
    \node (fig6t) at (40,30){
    Energy radiation \& Relativistic electrons \& Neutrons
    };
    \node (fig7) at (70,60){
    \centering{\includegraphics[width=0.1\paperwidth]{plane.pdf}}
    };
    \node (fig8) at (30,70){
    \centering{\includegraphics[width=0.1\paperwidth]{ballon.pdf}}
    };

    \end{tikzpicture}

\end{figure}
\end{frame}

\begin{frame}
\frametitle{History}
	\begin{columns}
		\begin{column}{0.5\textwidth}
			TGF --- short ($\sim 10$ mcs) flash of gamma-ray from thunderstorm cloud
		\end{column}
		\begin{column}{0.5\textwidth}
			TGE --- long-lasting (from 5 minutes to 3-4 hours)  enhancements of gamma-ray correlate with electric field changes  
		\end{column}
	\end{columns}
\centering\includegraphics[width=0.8\textwidth]{timeline.pdf}

@@

}%
\begin{frame}
    \frametitle{Reactor Like TGE model}

    \begin{figure} \centering
        \begin{tikzpicture}[      
        every node/.style={anchor=south west,inner sep=0pt},
        x=1mm, y=1mm
        ]   
        \node (fig1) at (0,0)
        { \centering\includegraphics[width=0.8\paperwidth]{draw.pdf}};
        \node[text width=6cm] (fig2) at (0,45)
        {
    \begin{itemize}
    \item Real cloud have multy-layer structure
    \item Electric field is non-uniform
    \item Consider cloud as system of cells
    \end{itemize}
    \centering\includegraphics[width=0.25\paperwidth]{cell.pdf}
     };  
        \node[text width=5cm] (fig3) at (54,47)
        {
            \begin{itemize}
            \item Seed gamma "burn" accelerator cells
            \item Secondary gamma propage in cloud
            \item Run chain reaction
            \item Evolution of reaction depend on local gain factor
            \end{itemize}

}; 
        \end{tikzpicture}

@@

\usebackgroundtemplate{}
\begin{frame}
\frametitle{Reactor Like TGE model}
\begin{columns}
    \begin{column}{0.5\textwidth}
        As simplification case consider mean global gain:
        \begin{itemize}
            \item  If global gain is $\large 1$ --- exponential rise up breakdown or local micro-breakdown
            \item If global gain is $\le 1$ --- exponential decay to background radiation
        \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
        \begin{figure}[htb]
            \centering
            \includegraphics[width=1\columnwidth]{aragats.png}
            \\
            \centering{Observation TGE on Aragats mount}
        \end{figure}

@@

\begin{frame}
    \frametitle{Proof of concept}
   	For fast checking the potential of our idea, we considered a next simplified model:  
    \begin{itemize}
    	\item There are only one tuning parameter  --- the local coefficient of gamma multiplication, describing usefulness of atmosphere for generating secondary particles;
    	\item Production of Gamma in cell occurs by Poisson distribution, momentum direction of generated gamma is defined by the electric field direction;
    	\item Electric field is chaotic: in point of cell ignition, direction of field is generated by uniform distribution, but magnitudes is constant for whole cloud;
    	\item Energy of particle not taken into account, propagation of gamma simulated with exponential distribution with fixed mean free path;
    	\item Cloud size is equals 1 kilometer and tracking of particle leaving volume stopped. 
    \end{itemize}
    This model is implemented as program on Kotlin programming language.
    \includegraphics[width=0.3\paperwidth]{kotlin.pdf}

\begin{frame}
    \frametitle{Results}
\begin{columns}
	\begin{column}{0.5\textwidth}
		\begin{figure}[htb]
		\centering
		\includegraphics[width=1\columnwidth]{proofTGF.pdf}
		\end{figure}
		{\LARGE This figure shows the case of an \textbf{explosive growth} in the number of secondary photons that are well suited to the phenomenon of \textbf{TGF}}
	\end{column}
	\begin{column}{0.5\textwidth}
		\begin{figure}[htb]
			\centering
			\includegraphics[width=1\columnwidth]{Extinction.pdf}
		\end{figure}
	{\LARGE 	This figure demonstrates the case when there was a \textbf{dissipation of an avalanche} that had just begun to develop.}

\begin{frame}
    \frametitle{Results}

@@

    	\begin{column}{0.6\textwidth}

    		\begin{figure}[htb]
    			\centering
    			\includegraphics[width=1\columnwidth]{proofTGE.pdf}
    		\end{figure}

    	\end{column}
    \end{columns}
    \centering{\huge This figure demonstrates the case of a \textbf{slower and less intensive growth}. Such processes with some minor adjustments and assumptions about field dynamics could describe \textbf{TGE} phenomenon.}
\end{frame}
